Winter weather on exam days and matriculation for a prestigious university in Japan

### 2021-04-03 Writeups/paper.tex
First draft done

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{gensymb, comment}
\usepackage{textcomp}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{setspace} 
\doublespacing
\usepackage{indentfirst}
\setlength{\parindent}{25pt}
\usepackage{bbm}
\usepackage{multicol}
\usepackage{makecell}
\usepackage{booktabs}
\newtheorem{prop}{Proposition} 
\newtheorem{assumption}{Assumption} 
\newtheorem{implication}{Implication} 
\usepackage{longtable}

@@

\title{Winter weather on exam days and admission for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
%\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The authors would like to thank Laura Schechter for her numerous feedback and support. We are also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions. Any errors in this draft are the sole responsibility of the authors.}}
\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu}}
\date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}

@@

  \medskip
  \vspace{1cm}
 \noindent Keywords: Temperature, Education, University admission, Cognitive performance
\end{abstract}

@@

External factors can impact various outcomes.
One active area of research is the effect of high temperature on performance at high-stakes exams.
Given the importance of high education for later outcomes, this is nice.

What is missing in the literature is the effect of \textit{low} temperature on performance at exams.

In this study, I analyze the effect of winter weathers on exam outcomes in Japan.
I use the weather on the days of National Center Test for University Admission (Center Test hereafter) and investigate its effect on the admission for the most prestigious university in Japan, the University of Tokyo (UTokyo henceforth).

If I use a middle-ranked university, reduction in admission share can be attributed to both lower and higher scores:
while students with lower scores can fail to get into the university, students with higher scores can choose to apply to and get admitted to higher-ranked universities.
Since UTokyo is the most prestigious university in Japan (** cite some university ranking **), it is unlikely that students who get high scores in Center Test go to better universities.\footnote{
  Medical departments in several universities are higher-ranked than UTokyo based on standard score.
  However, the career paths for those in the non-medical department of UTokyo and medical departments in universities are substantially different:
  while most students graduating from medical departments become medical doctors, the majority of students from UTokyo become bureaucrats, work for private firms, or go to graduate schools.
  Hence, it is unlikely that high scores at Center Test induce students who would otherwise get into UTokyo to go to a medical department.
}
Therefore, if I observe a reduction in admission share, I consider this as an evidence that the performance in Center Test is negatively affected.

\section{Background}

For admission for most (especially almost all public) universities, students are required to take two exams.
The first stage is Center Test.
Students take an exam on consecutive two days (Saturday and Sunday on mid January).
While different students can choose which subjects to take, most universities require students to take exams on math, English, language, natural science, and social science.
Questions are multiple-choice and common for all exam takers across Japan.
Exam takers do not receive their exact scores until the next May at earliest.
However, since they can record their answers to the exam booklets and can bring them back home, they know their scores by comparing their own answers and correct answers, which are made public through newspaper or websites of cramming schools.
High-school seniors take the test at designated cites in the area where their high schools are located.
On the other hand, high-school graduates are assigned to test cites in the area where the homes used in their application forms are located.

After taking Center Test, students apply for public and private universities.\footnote{
  There are private universities who accept applications before Center Test.
}
Applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students go to the universities and take the exam.
In other words, every applicant for a university takes the exam at the same location.

For public universities, there are three exam periods: the first one is typically at the end of February, the second one is on the first week of March, and the third one is typically around March 10th.
While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
UTokyo has two exam periods, the first and the third ones, although most of the admissions are provided for exam takers during the first exam period.

For UTokyo, scores at Center Test are used for two purposes.
First, the scores are used for eligibility to take the second-stage exam.
Thresholds varying across years and across majors are set, and if scores at Center Test are below the thresholds, students cannot take the second-stage exam.
Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.

Secondly, the scores at Center Test are taken into consideration for admission.
The final score of a students is calculated by the weighted average of exam scores at the first- and second-stage exams.

\section{Data}

I use two sets of data: weather and admission information for UTokyo.
For weather information, I get data from Japan Meteorological Agency.
Their website maintains the past weather across Japan.
In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6AM to 6PM.
Prefecture capitals tend to be most populated in each prefecture, and in many prefectures highly-ranked high schools from which many students go to UTokyo are located at prefecture capitals.
%\footnote{
%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
%}

For admission information for UTokyo, I use University Basic Information maintained by National Institution for Academic Degrees and Quality Enhancement of Higher Education.
This data contains information from 2012 to 2020 on the number of admitted students by prefectures at which their high schools are located.
I create the admission share of each prefecture, which is the ratio of the number of admitted students from a prefecture to the number of all admitted students.

The summary statistics are provided in Table \ref{tab:sum_stat}.
While the mean of the admission share (\%) is $2.08$,\footnote{
  Since there are admissions from abroad, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
} the distribution is starkly skewed.
As shown in Figure \ref{fig:admission_map}, many prefecture have less 1\% shares.
Also, the admission shares of the top 5 prefectures total more than 60\%.
This results in a small median admission share, $0.79$.

\begin{table}[H]
  \centering
  \caption{Summary Statistics}
  \resizebox{\linewidth}{!}{
  \input{"../Output/tex/sum_stat.tex"}
  }
  \label{tab:sum_stat}
  \footnotesize
  \begin{tablenotes}
    \item 
      Notes:
      Admission share (\%) is the share of newly admitted students to the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
  \end{tablenotes}
\end{table}

\begin{figure}[H]
  \centering
  \caption{Map of admission shares (\%) (average across years)}
  \includegraphics[width = 0.9\textwidth]{../Output/images/admission_map.png}
  \label{fig:admission_map}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      This map shows the admission shares (\%) for the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      Average of the shares across years is shown in the map.
      Although not shown in the legend due to the lack of the space, the lightest color in the map means the admission share between 0 to 0.5\% 
  \end{tablenotes}
\end{figure}

\section{Empirical Strategy}

The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the admission share for UTokyo.
The outcome variable, $Y_{jt}$ is the admission share (\%) for UTokyo of a prefecture $j$ in year $t$.
Let $T_{jt}$ be average temperature on exam days in $j$ in year $t$.
I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
I include other weather variables such as rainfall, snowfall, and cumulated snow on exam days as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

I run the following regression equation:
\begin{equation*}
  Y_{jt} = f(T_{jt}) + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
\end{equation*}
I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-variant factors and time-varying aggregate shocks through prefecture and year fixed effects.
As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variation in temperature on exam days.\footnote{
  Similar figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
}

One potential problem in the analysis is that a students from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam cites are measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get in any university for the first year and retake Center Test next year in his home prefecture.
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.

\section{Results}

@@

The main empirical results are provided in Table \ref{tab:main_reg}.
The column (1) shows the result with a linear specification.
While the point estimate is positive, which means admission shares are higher if an exam is held on warmer days, it is statistically insignificant. 
The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impacts of cold weather. 
Since the mean admission share is $2.08$\%, the coefficient on the lowest temperature bins means that reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the admission share decreases by 9\%.
Moreover, due to the stark skewness in the distribution of admission shares, the median admission share is $0.79$.
Therefore, the same temperature change decreases the admission share by 22\% of the median value.
Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in the column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
Although for a quite different temperature range, similar plateau effects are found in Park (2020) and Melo and Suzuki (2021).

In column (3) and (4), I add other weather variables.
While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the admission shares.
On the other hand, the cumulated snow on the ground has a negative impact.
To capture the effect of existence of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
This specification gives a result that, when there is snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the admission share by 0.13 percentage point.

In summary, I find a both statistically and economically significant impacts of weather on exam days.
In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impact on the admission shares for UTokyo.
In the next two subsections, I investigate the mechanisms underlying the findings.

\begin{table}[H]
  \center
  \caption{Regression: Admission share (\%) and weather on exam days}
  \input{"../Output/tex/main_reg.tex"}
  \label{tab:main_reg}
  \small
  \begin{tablenotes}
    \item
      The outcome variable is the admission shares (\%) for the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

@@

\begin{table}[H]
  \center
  \caption{Regression: Admission share (\%) and weather in the morning vs. during exam}
  \scriptsize
  \input{"../Output/tex/reg_morning_exam.tex"}
  \label{tab:reg_morning_exam}
  \scriptsize
  \begin{tablenotes}
    \item
      The outcome variable is the admission shares (\%) for the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      For variables in the morning, I use average weather variables at prefecture capitals between 6AM to 9AM on exam days.
      For variables during the exam, I use average weather variables at prefecture capitals between 9AM to 6PM on exam days.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

@@

\section{Conclusion}

In this paper I study the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
Instead of exam scores, I use the admission share for the most prestigious university in Japan, the University of Tokyo.
To identify the causal impact, I exploiting the variation in weathers at each prefecture on exam days.
Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains unknown.
This study fills the gap and identifies the causal impact of winter weather on the admission.

The results show that both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the admission share of a prefecture by 0.18 percentage point, which is 9\% of the mean admission share, or 22\% of the median admissions share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
Using the weathers in the morning and during the exams, I find a suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
This result suggest that adverse conditions for exam takers on the way to test cites affect their cognitive performance.

@@

Secondly, my results have implications on the admission process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measure to pick students.
Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
On the other hand, it may be effective to change the weights for Center Test and the second-stage exam.
Since the second-stage exam is held at each university, exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of college choice, it is desirable that universities take measures to mitigate the effect of nuisance factors on admission.

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{gensymb, comment}
\usepackage{textcomp}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage[sort]{natbib}
\usepackage{setspace} 
\doublespacing
\usepackage{indentfirst}
\setlength{\parindent}{25pt}
\usepackage{bbm}
\usepackage{multicol}
\usepackage{makecell}
\usepackage{booktabs}
\newtheorem{prop}{Proposition} 
\newtheorem{assumption}{Assumption} 
\newtheorem{implication}{Implication} 
\usepackage{longtable}

@@

\title{Winter weather on exam days and matriculation for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
%\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The author would like to thank Laura Schechter for her numerous feedback and support. I am also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions. Any errors in this draft are the sole responsibility of the author.}}
\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The authors would like to thank Laura Schechter for her numerous feedback and support.}}
\date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}

@@

  \medskip
  \vspace{1cm}
 \noindent Keywords: Temperature, Education, University matriculation, Cognitive performance
\end{abstract}

@@

Climate change is expected to increase the frequency of extreme weather events.
This is considered to have not only macro-level impacts but also micro-level impacts such as individual behaviors.
To understand the effect, emerging literature has studied effects of high temperature on various outcomes both in the long run and in the short run.
What has been less studied in the literature is the economic impact of \textit{low} temperature.
Given the possibility that the sea-ice loss, partly due to climate change, results in cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}, it is important to understand how low temperature can affect our lives.

This study analyzes the effect of winter weathers on exam outcomes in Japan.
Most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth), for admission.
Students take the exam on the same dates in mid-January in their prefectures.
This creates a variation in weathers to which they are exposed to on the exam dates.
I use the weather on the dates of Center Test and investigate its effect on the matriculation for the University of Tokyo (UTokyo henceforth).
The advantage of using the matriculation share for UTokyo as an outcome is that it is the most prestigious university in Japan.
This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance which could induce students to choose better universities.

The econometric analyses show that low temperature and snow cumulated on the ground on exam dates reduce the matriculation share.
The estimates are not only statistically but also economically significant.
Changing the temperature on the exam dates from 3-6 $^o$C to $<$ 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
Moreover, additional analyses suggest that the temperature in the morning on exam dates rather than temperature during exams impact exam performance. 
The results provide implications for effective measures to be taken to mitigate the negative impact of winter weathers.
These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admission process.

This study mainly contributes to the recent but growing literature of the effects of climate factors on the outcome of high-stakes exams.
Several previous studies have found the adverse effect of high temperature on learning, which reduces the performance at exams \citep{Park2020b, Cho2017}.
More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam days decreases the exam scores at high-stakes exams in China and the U.S., respectively.
Considering the importance of the effects the exam results can have on later life outcomes, it is important to understand how the external factors such as temperature affect exam performance and what we can do to ameliorate such effects.
To complement the literature, I investigate the effect of \textit{low} temperature on exam performance.

This study also has a contribution to the literature on the economic impact of low temperature.
It has been shown with controlled experiments that cold stresses negatively affect such things as cognitive ability and memory, as reviewed in \citet{Taylor2016}.
However, evidence based on data in the field is scarce.
Country-level studies have shown a non-linear effect of temperature on economic growth, in that both low and high temperature has a negative impact \citep{Burke2015}.
One study based on microdata is provided by \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
I use prefecture-level information to investigate how low temperature affects cognitive performance of exam takers.

This study proceeds as follows.
In Section \ref{sec:background}, the context of this study is introduced.
Section \ref{sec:data} describes the data. 
Our empirical strategy is introduced in Section \ref{sec:empirical_strategy}.
In Section \ref{sec:results}, I present the empirical results, and Section \ref{sec:conclusion} concludes.

\section{Background}\label{sec:background}

In Japan, for admission for most (almost all public) universities, students are required to take two exams.
The first-stage test is called Center Test.
Students take an exam on consecutive two days (Saturday and Sunday) on mid-January.
While different students can choose which subjects to take, most public universities require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
Questions are multiple-choice and common for all exam takers across Japan.
High-school seniors take the test at designated cites in the area where their high schools are located.
On the other hand, high-school graduates are assigned to test cites in the area where the homes used in their application forms are located.

Exam takers do not receive their scores until the next May at earliest.
However, they can record their answers on their exam booklets and can bring them back home.
Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cramming schools.
After taking Center Test, students apply for public and private universities.\footnote{
  There are private universities who accept applications before Center Test.
}
Applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students physically go to the universities and take the exam.
Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.

Most public universities, including UTokyo, have three periods for the second-stage exam:
usually, the first one is at the end of February, the second one is on the first week of March, and the third one is on the second week of March.
Students can apply for only one university at each exam period.
While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
Up to 2015, UTokyo had two exam periods, the first and the third ones, although most of the admissions were provided for exam takers at the first exam period.\footnote{
  In 2015, while 3,008 students got admitted though the first-period exam, only 100 students got admitted through the third-period exam.
  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01_h27.html
}
In 2016, UTokyo abolished the third-period exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test.
In the latter process, students take interviews on November before Center Test, and after taking Center Test, final admissions are determined based on the results both of interviews and scores at Center Test.\footnote{
  In 2020, among 3,083 admitted students, only 73 students got admitted through this process.
  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01.html
}

In admission for UTokyo, scores at Center Test are used for two purposes for the first-period exam takers.
First, the scores are used for eligibility to take the second-stage exam.
Thresholds varying across years and across majors are set, and if scores at Center Test are below the thresholds, students cannot take the second-stage exam.
Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.
Secondly, the scores at Center Test are taken into consideration for admission.
The final score of a students is calculated by the weighted sum of exam scores at the first- and the second-stage exams.\footnote{
  In 2020, for the first-period exam takers, the weights for Center Test and the second-stage exam are 20\% and 80\%.
  Also, until 2015, for the third-period exam takers, scores at Center Test were used only for eligibility and were not accounted for the final admission.
}

In summary, results at Center Test are crucial for applicants for UTokyo.
This study will investigate how external factors such as temperature and weather on the dates of Center Test affect matriculation for UTokyo.

\section{Data}\label{sec:data}

I use two sets of data: weather and matriculation information for UTokyo.
For weather information, I get data from \Citeauthor{jma}.
Their website maintains the past weather across Japan.
In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6AM to 6PM.
Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
%\footnote{
%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
%}

For matriculation information for UTokyo, I use University Basic Information maintained by \Citeauthor{univ_info}.
This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
I create the matriculation share of each prefecture, which is the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and decision to go to the university or not.
  Due to the lack of the number of admitted students by prefecture, I use the information on matriculation.
  For UTokyo, the number of admissions and the number of matriculations are very close:
  In 2020, among 3,083 admitted students, 3,064 students matriculate at UTokyo.
  Moreover, it is unlikely that weathers on exam days affect decisions of admitted students to matriculate or not.
}

The summary statistics are provided in Table \ref{tab:sum_stat}.
While the mean of the matriculation share (\%) is $2.08$,\footnote{
  Since there are matriculations from abroad, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
  I do not consider matriculations from abroad in the analyses since their admission is mostly based on interviews and essays.
} the distribution is starkly skewed.
As shown in Figure \ref{fig:admission_map}, many prefecture have less 1\% shares.
Also, the matriculation shares of the top 5 prefectures total more than 60\%.
This results in a small median matriculation share, $0.79 \%$.

%\begin{table}[H]
%  \centering
%  \caption{Summary Statistics}
%  \resizebox{0.8\linewidth}{!}{
%  \input{"../Output/tex/sum_stat.tex"}
%  }
%  \label{tab:sum_stat}
%  \footnotesize
%  \begin{tablenotes}
%    \item 
%      Notes:
%      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
%  \end{tablenotes}
%\end{table}

%\begin{figure}[H]
%  \centering
%  \caption{Map of matriculation shares (\%) (average across years)}
%  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
%  \label{fig:admission_map}
%  \footnotesize
%  \begin{tablenotes}
%    \item Notes:
%      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      Average of the shares across years is shown in the map.
%      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
%  \end{tablenotes}
%\end{figure}

\section{Empirical Strategy}\label{sec:empirical_strategy}

The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the matriculation share for UTokyo.
The reason why I use the matriculation share for UTokyo is as follows:
consider an matriculation share for a middle-ranked university.
Suppose also that low temperature has a negative impact on exam scores.
Then, 
(i) students from the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
(ii) students from the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
However, the second effect is unlikely to be large for UTokyo for the following reasons.
First, UTokyo is known to be the best university in Japan.
Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
}
Therefore, I can rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.

In the analyses, the outcome variable, $Y_{jt}$ is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
Let $T_{jt}$ be average temperature on exam days in $j$ in year $t$.
I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
I include other weather variables such as rainfall, snowfall, and cumulated snow on exam days as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

I run the following regression equation:
\begin{equation*}
  Y_{jt} = f(T_{jt}) + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
\end{equation*}
I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-variant factors and time-varying aggregate shocks through prefecture and year fixed effects.
As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam days.\footnote{
  Similar figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
}

One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam cites are measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get in any university for the first year and retake Center Test next year in his home prefecture.
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.

%\begin{figure}[H]
%  \centering
%  \caption{Average temperature on two exam days in each prefecture each year}
%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
%  \label{fig:temperature_diff}
%  \footnotesize
%  \begin{tablenotes}
%    \item Notes:
%      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
%      Average across two test days in each year is shown in the figure.
%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
%  \end{tablenotes}
%\end{figure}

\section{Results}\label{sec:results}

@@

The main empirical results are provided in Table \ref{tab:main_reg}.
The standard errors are clustered at the prefecture level.
The column (1) shows the result with a linear specification.
While the point estimate is positive, which means matriculation shares are higher if an exam is held on warmer days, it is statistically insignificant. 
The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impacts of cold weather. 
Since the mean matriculation share is $2.08$\%, the coefficient on the lowest temperature bins means that reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the matriculation share decreases by 9\%.
Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$.
Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in the column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.

In column (3) and (4), I add other weather variables.
While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the matriculation shares.
On the other hand, the cumulated snow on the ground has a negative impact.
To capture the effect of existence of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
This specification gives a result that, when there is snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the matriculation share by 0.13 percentage point.

In summary, I find a both statistically and economically significant impacts of weather on exam days.
In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impact on the matriculation shares for UTokyo.
In the next two subsections, I investigate the mechanisms underlying the findings.

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather on exam days}
%  \input{"../Output/tex/main_reg.tex"}
%  \label{tab:main_reg}
%  \small
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

@@

Here I investigate if the findings above are due to weathers in the morning or during the exams.
This distinction can be important since different measures should be taken to mitigate the effect of each weather.
The results are shown in Table \ref{tab:reg_morning_exam}.
Columns (1) and (2) show statistically significant impact of low temperature in the morning.
On the other hand, statistically insignificant estimates are obtained in columns (3) and (4) with weathers during the exams, although the magnitudes are large.
Also, including both weathers simultaneously, column (5) shows the negative and significant impact of cold weather in the morning on the matriculation share.\footnote{
  Estimates for cumulated snow are insignificant in column (5) due to multicollinearity, which blows up their standard errors.
  Their correlation coefficient is 0.99.
  This is reasonable since their differences can be caused by new snowfall or snow melting, which cannot happen drastically within hours.
}
This suggests that the morning weathers on the exam dates matter for exam performance.

@@

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
%  \scriptsize
%  \input{"../Output/tex/reg_morning_exam.tex"}
%  \label{tab:reg_morning_exam}
%  \scriptsize
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      For variables in the morning, I use average weather variables at prefecture capitals between 6AM to 9AM on exam days.
%      For variables during the exam, I use average weather variables at prefecture capitals between 9AM to 6PM on exam days.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

\section{Conclusion}\label{sec:conclusion}

In this paper I study the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
Instead of exam scores, I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
To identify the causal impact, I exploit the variation in weathers at each prefecture on exam days.
Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
This study fills the gap and identifies the causal impact of winter weather on the matriculation.

The results show that both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
Using the weathers in the morning and during the exams, I find a suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
This result suggest that adverse conditions for exam takers on the way to test cites affect their cognitive performance.

@@

Secondly, my results have implications on the matriculation process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measure to select students.
Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
On the other hand, it may be effective to change the weights for Center Test and the second-stage exam.
Since the second-stage exam is held at each university, all exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on matriculation.

\clearpage
\bibliographystyle{apalike}
\bibliography{todai}

\section{Figures}

\begin{figure}[H]
  \centering
  \caption{Map of matriculation shares (\%) (average across years)}
  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
  \label{fig:admission_map}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      Average of the shares across years is shown in the map.
      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
  \end{tablenotes}
\end{figure}

\section{Tables}

\begin{table}[H]
  \centering
  \caption{Summary Statistics}
  \resizebox{0.8\linewidth}{!}{
  \input{"../Output/tex/sum_stat.tex"}
  }
  \label{tab:sum_stat}
  \footnotesize
  \begin{tablenotes}
    \item 
      Notes:
      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
  \end{tablenotes}
\end{table}
